---
title: "Homework #1 -- Pet Names Dataset"Rana alshammari
author: "Musab Isah\n"
date: "`r Sys.Date()`"
output: github_document
---

**Student ID:insert ID here**2201000999

**Deadline:** 23:59 on Saturday, 13 February 2021

**Total Points:** 30


## Loading Packages

```{r load-packages, message = FALSE}

library(tidyverse)
library(openintro)
library(ggrepel)
```


##Exercises

`1.According to the data dictionary, how many pets are included in this dataset?


(4 points)
```{r}

```
Write your narrative here

Answer1(52519 pets)

`2.Again, according to the data dictionary, how many variables do we have for each pet?

(4 points)

```{r}

```
Write your narrative below

Answer2(7)
`3. Copy the code provided in the homework documentation and paste it here. 

(4 points)

```{r}
seattlepets %>%
count(animal_name, sort = TRUE)

```
Write your narrative here
NA        483
Lucy      439
Charlie   387
Luna      355

`4.

(10 points)

```{r species-name-top5, eval=TRUE}
seattlepets %>%
group_by(species) %>%
count(animal_name, sort = TRUE) %>%
slice_max(n, n = 5) %>% arrange(species, n)

```

`5.  What names are more common for cats than dogs? The ones above the line or the ones below the line?

Answer here
oliver and lily
(4 points)

`6. Is the relationship between the two variables (proportion of cats with a given name and proportion of dogs with a given name) positive or negative? What does this mean in context of the data?

Answer here
positive,,if doge names increase the cats names increase also if dogs name Decrease the cats name Decrease also in the same of them 
(4 points)

